Connecting R with D3 for dynamic graphics, to explore multivariate data with tours

### 2019-03-04 paper-tourrd3.Rmd
code reformatting

```
observe({
      if (length(rv$mat[1, ]) < 3) {
        session$sendCustomMessage(type = "debug",
        message = "Error: Need >2 variables.")
      }
      aps <- rv$aps
      tour <- rv$tour
      step <- rv$tour(aps / fps)
      invalidateLater(1000 / fps)
      j <- center(rv$mat %*% step$proj)
      j <- cbind(j, class = rv$class)
      colnames(j) <- NULL
      session$sendCustomMessage(type = "data",
                                message =
                                list(d = toJSON(data.frame(pL=rv$pLabel[,1],x=j[,2],y=j[,1],c=j[,3])),
                                a = toJSON(data.frame(n=rv$vars,y=step$proj[,1],x=step$proj[,2]))))
})
```

>>>>

```{r eval=FALSE, echo=TRUE}
observe({
    if (length(rv$mat[1, ]) < 3) {
      session$sendCustomMessage(type = "debug",
      message = "Error: Need >2 variables.")
    }
    aps <- rv$aps
    tour <- rv$tour
    step <- rv$tour(aps / fps)
    invalidateLater(1000 / fps)
    j <- center(rv$mat %*% step$proj)
    j <- cbind(j, class = rv$class)
    colnames(j) <- NULL
    session$sendCustomMessage(type = "data",
         message = list(d = toJSON(data.frame(pL=rv$pLabel[,1], x=j[,2], 
                                              y=j[,1], c=j[,3])),
                        a = toJSON(data.frame(n=rv$vars, y=step$proj[,1], 
                                              x=step$proj[,2]))))
})
```

### 2019-03-04 paper-tourrd3.tex
code reformatting

\begin{verbatim}
observe({
      if (length(rv$mat[1, ]) < 3) {
        session$sendCustomMessage(type = "debug",
        message = "Error: Need >2 variables.")
      }
      aps <- rv$aps
      tour <- rv$tour
      step <- rv$tour(aps / fps)
      invalidateLater(1000 / fps)
      j <- center(rv$mat %*% step$proj)
      j <- cbind(j, class = rv$class)
      colnames(j) <- NULL
      session$sendCustomMessage(type = "data",
                                message =
                                list(d = toJSON(data.frame(pL=rv$pLabel[,1],x=j[,2],y=j[,1],c=j[,3])),
                                a = toJSON(data.frame(n=rv$vars,y=step$proj[,1],x=step$proj[,2]))))
})
\end{verbatim}

>>>>

\begin{Schunk}
\begin{Sinput}
observe({
    if (length(rv$mat[1, ]) < 3) {
      session$sendCustomMessage(type = "debug",
      message = "Error: Need >2 variables.")
    }
    aps <- rv$aps
    tour <- rv$tour
    step <- rv$tour(aps / fps)
    invalidateLater(1000 / fps)
    j <- center(rv$mat %*% step$proj)
    j <- cbind(j, class = rv$class)
    colnames(j) <- NULL
    session$sendCustomMessage(type = "data",
         message = list(d = toJSON(data.frame(pL=rv$pLabel[,1], x=j[,2], 
                                              y=j[,1], c=j[,3])),
                        a = toJSON(data.frame(n=rv$vars, y=step$proj[,1], 
                                              x=step$proj[,2]))))
})
\end{Sinput}
\end{Schunk}
